---
title: "trial_number_stats"
author: "CC"
date: "2023-04-28"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Stats on ERP trial number

setup
```{r, echo=FALSE}

library("tidyverse")
library("readxl")
library("rstatix")

rm(list=ls())

load("./../../data/ERP/tidied/erp_individual_trial.RData")

```

## Count number of trials for each subject, each component, and each condition
```{r, echo=FALSE}
# Trial # stats -----
n_trial_subj <- data_erp_all_indi_trial %>%
  group_by(subj_num, time_point, component, cond) %>%
  summarise(n_trial_individual = n()) %>%
  ungroup() %>%
  mutate(order =
           case_when(
             cond %in% c(1, 3, 5) ~ "increase",
             cond %in% c(2, 4, 6) ~ "decrease")) %>%
  mutate(order = factor(order),
         cond = factor(cond)) %>% 
  distinct_at(vars(-component)) %>% # Component doesnt seem to matter - numbers are the same across components. Remove redundant info. 
  unite("uID", subj_num, time_point, sep = "_", remove = F, na.rm = FALSE) %>%
  mutate(uID = factor(uID)) # Add unique ID column.
```


## Calculate the mean, sd, and range for the number of trials per subject for each of the 6 conditions
```{r, echo=FALSE}
n_trial_cond <- n_trial_subj %>%
  group_by(cond) %>%
  summarise(mean_n_trial_cond = mean(n_trial_individual),
            sd_n_trial_cond = sd(n_trial_individual),
            range_min = min(n_trial_individual),
            range_max = max(n_trial_individual)) %>%
  ungroup() 
```

```{r}
n_trial_cond
```

## Inferential Stats
### Are there differences in the number of trials across the six conditions? - No
```{r}
aov.cond <- aov(n_trial_individual~factor(cond)+Error(factor(uID)), data = n_trial_subj)
summary(aov.cond)
```

### Are there differences in the number of increasing vs. decreasing trials? - No
```{r}
aov.order <- aov(n_trial_individual~factor(order)+Error(factor(uID)), data = n_trial_subj)
summary(aov.order)
```

